---
title: 'Shiny app at daily frequency'
format: html
---




**Libraries (necessary)**:

```{r}
if (!require("pacman")) install.packages("pacman")
pacman::p_load(
  here,        # here()
  arrow,       # open_dataset(), read_parquet(), write_parquet(), collect()
  sfarrow,     # st_read_parquet()
  sf,          # st_drop_geometry()
  dplyr,       # rename, mutate, case_when, if_else, left_join, relocate,
               # filter, select, group_by, summarise, arrange, pull, ungroup, n
  tibble,      # tibble()
  tidyr,       # complete()
  lubridate,   # floor_date()
  stringr,     # str_pad()
  restatis     # gen_logincheck(), gen_table()
)
```



# 1. datasets
> Here there is a list of the datasets you can use to create the shiny app.


## 1.1. Dataset of daily registrations
> here there is the dataset to see the daily registration of balcony PVs over time.


Create the datasets:
```{r}
data <- open_dataset(here("3. subsidy programs/3.1. data/EinheitenSolar.parquet"))


# Step 1: rename German → English (explicit mapping, column order differs from old dataset)
data <- data |>
  rename(
    UnitMastrNumber                          = EinheitMastrNummer,
    DateLastUpdate                           = DatumLetzteAktualisierung,
    LocationMastrNumber                      = LokationMaStRNummer,
    GridOperatorVerificationStatus           = NetzbetreiberpruefungStatus,
    GridOperatorVerificationDate             = NetzbetreiberpruefungDatum,
    PlantOperatorMastrNumber                 = AnlagenbetreiberMastrNummer,
    Country                                  = Land,
    FederalState                             = Bundesland,
    District                                 = Landkreis,
    Municipality                             = Gemeinde,
    MunicipalityCode                         = Gemeindeschluessel,
    PostalCode                               = Postleitzahl,
    City                                     = Ort,
    RegistrationDate                         = Registrierungsdatum,
    CommissioningDate                        = Inbetriebnahmedatum,
    UnitSystemStatus                         = EinheitSystemstatus,
    UnitOperationalStatus                    = EinheitBetriebsstatus,
    NotPresentInMigratedUnits                = NichtVorhandenInMigriertenEinheiten,
    PowerGenerationUnitName                  = NameStromerzeugungseinheit,
    Weic_NotAvailable                        = Weic_nv,
    PowerPlantNumber_NotAvailable            = Kraftwerksnummer_nv,
    EnergySource                             = Energietraeger,
    GrossCapacity                            = Bruttoleistung,
    NetNominalCapacity                       = Nettonennleistung,
    RemoteControllabilityGridOperator        = FernsteuerbarkeitNb,
    FeedInType                               = Einspeisungsart,
    AssignedActivePowerInverter              = ZugeordneteWirkleistungWechselrichter,
    NumberOfModules                          = AnzahlModule,
    TypeOfSolarSystem                        = ArtDerSolaranlage,
    PowerLimitation                          = Leistungsbegrenzung,
    UniformOrientationAndTiltAngle           = EinheitlicheAusrichtungUndNeigungswinkel,
    MainOrientation                          = Hauptausrichtung,
    MainOrientationTiltAngle                 = HauptausrichtungNeigungswinkel,
    UsageArea                                = Nutzungsbereich,
    EegMastrNumber                           = EegMaStRNummer,
    StorageAtSameLocation                    = SpeicherAmGleichenOrt,
    SecondaryOrientation                     = Nebenausrichtung,
    SecondaryOrientationTiltAngle            = NebenausrichtungNeigungswinkel,
    Street                                   = Strasse,
    StreetNotFound                           = StrasseNichtGefunden,
    HouseNumber_NotAvailable                 = Hausnummer_nv,
    HouseNumberNotFound                      = HausnummerNichtGefunden,
    Longitude                                = Laengengrad,
    Latitude                                 = Breitengrad,
    DateStartTemporaryDecommissioning        = DatumBeginnVoruebergehendeStilllegung,
    HouseNumber                              = Hausnummer,
    AddressAddition                          = Adresszusatz,
    RemoteControllabilityDirectMarketer      = FernsteuerbarkeitDv,
    PreviousPlantOperatorMastrNumber         = AltAnlagenbetreiberMastrNummer,  # new variable
    DateOfOperatorChange                     = DatumDesBetreiberwechsels,
    DateRegistrationOfOperatorChange         = DatumRegistrierungDesBetreiberwechsels,
    CadastralDistrict                        = Gemarkung,
    FieldParcelNumbers                       = FlurFlurstuecknummern,
    ConnectionToExtraHighOrHighVoltage       = AnschlussAnHoechstOderHochSpannung,
    DatePermanentDecommissioning             = DatumEndgueltigeStilllegung,
    SizeOfUsedAreaInHectares                 = GroesseDerInAnspruchGenommenenFlaecheInHektar,
    PreviousUsageTypeOfArea                  = VorherigerNutzungsartenbereichDerFlaeche,
    PredominantUsageTypeBeforeSolarConstruction = UeberwiegendeNutzungsartDerFlaecheVorErrichtung,
    NameOfSolarPark                          = NameDesSolarparks,
    AdditionalFeaturesOfAreaAndCurrentUsage  = ZusaetzlicheMerkmaleDerFlaecheUndDerAktuellenFlaechennutzung,
    GenMastrNumber                           = GenMastrNummer,
    CommissioningDateAtCurrentLocation       = InbetriebnahmedatumAmAktuellenStandort,
    DispatchResponsible                      = Einsatzverantwortlicher,
    CitizenEnergy                            = Buergerenergie,
    DateResumptionOfOperation                = DatumWiederaufnahmeBetrieb,
    PlannedCommissioningDate                 = GeplantesInbetriebnahmedatum,
    ClearanceHeight                          = LichteHoehe,
    PowerPlantNumber                         = Kraftwerksnummer
  )

# Step 2: convert numeric columns (XML parsing stores everything as character)
data <- data |>
  mutate(
    TypeOfSolarSystem           = as.integer(TypeOfSolarSystem),
    Country                     = as.integer(Country),
    FederalState                = as.integer(FederalState),
    GrossCapacity               = as.numeric(GrossCapacity),
    NetNominalCapacity          = as.numeric(NetNominalCapacity),
    AssignedActivePowerInverter = as.numeric(AssignedActivePowerInverter),
    NumberOfModules             = as.integer(NumberOfModules)
  )

# Step 3: lookup tables
C1 <- data.frame(
  TypeOfSolarSystem.names = c(
    "Structural_facilities", "Other_Structural_facilities", "Open_space",
    "Bodies_water", "Large_parking_lot", "Plug_in_sola_system", "Onshore&Offshore_wind_power"
  ),
  TypeOfSolarSystem = as.integer(c(853, 2484, 852, 3002, 3058, 2961, NA))
)

C2 <- tibble(
  Country = as.integer(c(84, 231, 90, 66, 198, 206, 106)),
  Country.sn = c("Germany", "Switzerland", "Denmark", "Belgium", "Netherlands", "Austria", "France")
)

C3 <- data.frame(
  FederalState = as.integer(c(
    1409, 1402, 1400, 1403, 1412, 1408, 1410, 1407,
    1414, 1411, 1413, 1405, 1415, 1406, 1401, 1404
  )),
  FederalState.names = c(
    "North Rhine-Westphalia", "Baden-Württemberg", "Brandenburg", "Bavaria",
    "Saarland", "Lower Saxony", "Rhineland-Palatinate", "Mecklenburg-Western Pomerania",
    "Saxony-Anhalt", "Schleswig-Holstein", "Saxony", "Hesse",
    "Thuringia", "Hamburg", "Berlin", "Bremen"
  ),
  FederalStateCode = c(
    "DEA", "DE1", "DE4", "DE2",
    "DEC", "DE9", "DEB", "DEM",
    "DEE", "DEF", "DED", "DE7",
    "DEG", "DE6", "DE3", "DE5"
  )
)

# district code from map (no geometry needed)
districts_map <- st_read_parquet(here("ignore/2. maps/districts.parquet")) |>
  st_drop_geometry() |>
  select(District, DistrictCode)

# Step 4: join lookups
data <- data |>
  left_join(C1, by = "TypeOfSolarSystem") |>
  relocate(TypeOfSolarSystem.names, .after = TypeOfSolarSystem) |>
  left_join(C2, by = "Country") |>
  relocate(Country.sn, .after = Country) |>
  left_join(C3, by = "FederalState") |>
  relocate(FederalState.names, .after = FederalState) |>
  relocate(FederalStateCode, .after = FederalState.names) |>
  left_join(districts_map, by = "District") |>
  relocate(DistrictCode, .after = District)

# Step 5: solar_category
reform_date <- as.Date("2024-05-16")

data <- data |>
  mutate(
    RegistrationDate  = as.Date(RegistrationDate),
    CommissioningDate = as.Date(CommissioningDate),
    solar_category = case_when(
      TypeOfSolarSystem == 2961 & RegistrationDate <  reform_date & AssignedActivePowerInverter <= 0.6 ~ "Plug_in_sola_system - Balcony",
      TypeOfSolarSystem == 2961 & RegistrationDate >= reform_date & AssignedActivePowerInverter <= 0.8 & GrossCapacity <= 2.0 ~ "Plug_in_sola_system - Balcony",
      TypeOfSolarSystem == 2961 ~ "Plug_in_sola_system - Non-Balcony",
      TRUE ~ TypeOfSolarSystem.names
    )
  )
# Step 6: filter Germany
data <- data |>
  filter(Country.sn == "Germany")

# Step 7: date variables (week, month, quarter, year)
data <- data |>
  mutate(
    date.registration.day     = RegistrationDate,
    date.registration.week    = floor_date(RegistrationDate,  "week"),
    date.registration.month   = floor_date(RegistrationDate,  "month"),
    date.registration.quarter = floor_date(RegistrationDate,  "quarter"),
    date.registration.year    = floor_date(RegistrationDate,  "year"),
    date.commission.day       = CommissioningDate,
    date.commission.week      = floor_date(CommissioningDate, "week"),
    date.commission.month     = floor_date(CommissioningDate, "month"),
    date.commission.quarter   = floor_date(CommissioningDate, "quarter"),
    date.commission.year      = floor_date(CommissioningDate, "year")
  )

# Step 8: fix MunicipalityCode
data <- data |>
  mutate(MunicipalityCode = str_pad(as.character(MunicipalityCode), 8, pad = "0"))


# Collapse every category other than `Balcony PVs` into a single `Non-balcony PVs` group:
data <- data |>
  mutate(solar_category = if_else(solar_category == "Plug_in_sola_system - Balcony",
                                  "Balcony PVs",
                                  "Non-balcony PVs"))

# Here I want to filter for the balcony PVs:
data <- data |>
  filter(solar_category == "Balcony PVs")
```

Create the dataset daily frequency for all municipalities:

```{r}
data_day <- data |>
  group_by(MunicipalityCode, Municipality, date.registration.day) |>
  summarise(n = n(), .groups = "drop") |>
  collect() |>
  group_by(MunicipalityCode, Municipality) |>
  complete(date.registration.day = seq(min(date.registration.day), max(date.registration.day), by = "day"), fill = list(n = 0)) |>
  arrange(MunicipalityCode, date.registration.day) |>
  mutate(n_cumulative = cumsum(n)) |>
  ungroup()
```

***Population***:

```{r}
#Credentials:
# gen_auth_save(database = 'genesis')
# gen_auth_save(database = 'regio')

gen_logincheck(database = "genesis")
gen_logincheck(database = "regio")


# Load the data:
pop.muni.2023 <- gen_table(
  name      = "12411-01-01-5",
  database  = "regio",
  language  = "en",
  startyear = 2023,
  endyear   = 2023
) |>
  filter(`1_variable_code` == "GEMEIN",          # municipalities only (drops DINSG/DLAND/REGBEZ/KREISE)
         is.na(`2_variable_attribute_code`)) |>  # sex total
  select(
    MunicipalityCode = `1_variable_attribute_code`,
    Municipality     = `1_variable_attribute_label`,
    year             = time,
    population       = value
  ) |>
  mutate(
    date       = as.Date(paste0(substr(year, 1, 4), "-12-31")),
    population = suppressWarnings(as.numeric(population))
  ) |>
  select(Municipality, MunicipalityCode, date, population) 
```


***Adjust for the population data***:

```{r}
pop.muni.2023 <- pop.muni.2023 |> filter(!is.na(population))

data_day <- data_day |>
  filter(MunicipalityCode %in% pop.muni.2023$MunicipalityCode) |>
  left_join(pop.muni.2023 |> select(MunicipalityCode, population),
            by = "MunicipalityCode") |>
  mutate(
    n_per100k            = (n            / population) * 100000,
    n_cumulative_per100k = (n_cumulative / population) * 100000
  )
```

***load the dataset***:

```{r}
write_parquet(
  data_day,
  here("3. subsidy programs/3.4. shiny app/2. shiny apps/3/outcome_variable.parquet")
)

data_day <- read_parquet(
  here("3. subsidy programs/3.4. shiny app/2. shiny apps/3/outcome_variable.parquet")
)
```





## 1.2. dataset for bounderies
> Here I want to load the datasets for the bounderis, i.e., for municipalities and federal states.

**Dataset for municipalities**:

```{r}
municipalities <- st_read_parquet(here("3. subsidy programs", "3.4. shiny app", "2. shiny apps", "3", "municipalities.parquet"))
glimpse(municipalities)
```



**Dataset for federal states**:

```{r}
federal_states <- st_read_parquet(here("3. subsidy programs", "3.4. shiny app", "2. shiny apps", "3", "federalState.parquet"))
glimpse(federal_states)
```


## 1.3. Treatment dataset
> Here you have the dataset where you can see for some of the municipalities which ones implemented a subsidy program for adoption of balcony PVs.

First I want to create the treatment dataset. Later I will check if there is match for municiplaities in the dataset of the population data.

Treatment dataset:

```{r}
# Full date range
all_dates <- seq.Date(as.Date("2019-02-01"), as.Date("2025-11-01"), by = "month")

# All municipalities (Survey names take priority over Ben names for overlapping codes)
muni_all <- tribble(
  ~Municipality,                    ~MunicipalityCode,
  # From Survey
  "Bonn, Stadt",                    "05314000",
  "Darmstadt, Wissenschaftsstadt",  "06411000",
  "Frankfurt am Main, Stadt",       "06412000",
  "Oldenburg (Oldenburg), Stadt",   "03403000",
  "Jever, Stadt",                   "03455007",
  "Fröndenberg/Ruhr, Stadt",        "05978012",
  "Weilheim i.OB, St",             "09190157",
  "Kamp-Lintfort, Stadt",          "05170020",
  "Lüneburg, Hansestadt",           "03355022",
  "Friedrichshafen, Stadt",         "08435016",
  "Kornwestheim, Stadt",            "08118046",
  "Erlangen",                       "09562000",
  "Wickede (Ruhr)",                 "05974056",
  # From Heidelberg
  "Heidelberg, Stadt",              "08221000",
  # From Ben (not in Survey)
  "Stuttgart",                      "08111000",
  "Koln",                           "05315000",
  "Braunschweig",                   "03101000",
  "Munchen",                        "09162000",
  "Berlin",                         "11000000",
  "Essen",                          "05113000",
  "Dresden",                        "14612000",
  "Duisburg",                       "05112000",
  "Dortmund",                       "05913000",
  "Bremen",                         "04011000",
  "Bremerhaven",                    "04012000",
  "Hamburg",                         "02000000",
  "Reutlingen",                     "08415061",
  "Erfurt",                         "16051000",
  "Hannover",                       "03241001",
  "Munster",                        "05515000"
)

# Create full balanced panel
data.treatment <- crossing(
  MunicipalityCode = muni_all$MunicipalityCode,
  date = all_dates
) |>
  left_join(muni_all, by = "MunicipalityCode") |>
  mutate(
    treatment = case_when(
      # --- Survey municipalities (priority 1) ---
      MunicipalityCode == "05314000" & date >= as.Date("2021-09-01") ~ 1L,
      MunicipalityCode == "06411000" & date >= as.Date("2021-07-01") ~ 1L,
      MunicipalityCode == "06412000" & date >= as.Date("2023-11-01") & date <= as.Date("2024-03-01") ~ 1L,
      MunicipalityCode == "03403000" & date >= as.Date("2020-01-01") & date <= as.Date("2023-03-01") ~ 1L,
      MunicipalityCode == "03455007" & date >= as.Date("2023-01-01") & date <= as.Date("2023-12-01") ~ 1L,
      MunicipalityCode == "05978012" & date >= as.Date("2022-03-01") & date <= as.Date("2023-12-01") ~ 1L,
      MunicipalityCode == "09190157" & date >= as.Date("2022-04-01") & date <= as.Date("2024-12-01") ~ 1L,
      MunicipalityCode == "05170020" & date >= as.Date("2021-11-01") & date <= as.Date("2024-03-01") ~ 1L,
      # --- Heidelberg (priority 2) ---
      MunicipalityCode == "08221000" & date >= as.Date("2022-09-01") & date <= as.Date("2024-03-01") ~ 1L,
      # --- Ben-only municipalities (priority 3) ---
      MunicipalityCode == "08111000" & date >= as.Date("2020-11-01") & date <= as.Date("2025-12-01") ~ 1L,
      MunicipalityCode == "05315000" & date >= as.Date("2022-04-01") ~ 1L,
      MunicipalityCode == "03101000" & date >= as.Date("2022-04-01") ~ 1L,
      MunicipalityCode == "09162000" & date >= as.Date("2022-10-01") ~ 1L,
      MunicipalityCode == "11000000" & date >= as.Date("2023-02-01") ~ 1L,
      MunicipalityCode == "05113000" & date >= as.Date("2023-03-01") ~ 1L,
      MunicipalityCode == "14612000" & date >= as.Date("2023-06-01") ~ 1L,
      MunicipalityCode == "05112000" & date >= as.Date("2023-10-01") ~ 1L,
      MunicipalityCode == "05913000" & date >= as.Date("2023-11-01") ~ 1L,
      TRUE ~ 0L
    )
  ) |>
  select(Municipality, MunicipalityCode, date, treatment) |>
  arrange(Municipality, MunicipalityCode, date) |>
  group_by(MunicipalityCode) |>
  mutate(ever_treated = max(treatment)) |>
  ungroup()

# Save and load the treatment dataset:

write_parquet(
  data.treatment,
  here("3. subsidy programs/3.4. shiny app/2. shiny apps/3/data.treatment.parquet")
)

data.treatment <- read_parquet(
  here("3. subsidy programs/3.4. shiny app/2. shiny apps/3/data.treatment.parquet")
)
```

Check:

```{r}
# dataset with the municiplaities
pop.muni.2023


# perform the check
# Are all MunicipalityCodes in data.treatment present in pop.muni.2023?
missing <- setdiff(unique(data.treatment$MunicipalityCode),
                   pop.muni.2023$MunicipalityCode)

cat("Distinct municipalities in data.treatment:", n_distinct(data.treatment$MunicipalityCode), "\n")
cat("Of which present in pop.muni.2023:        ",
    n_distinct(data.treatment$MunicipalityCode) - length(missing), "\n")
cat("Missing in pop.muni.2023:                 ", length(missing), "\n\n")

if (length(missing) > 0) {
  cat("First 20 missing MunicipalityCodes:\n")
  print(head(missing, 20))
}
```