---
title: 'Shiny app at daily frequency'
format: html
---

> Here I want to create the dataset for Germany.


**Claude chat**:
- SHINY APP (2)


**Shiny app**:
I want to create a shiny app where I can see:
- on the left there is a map of all the municipalities included in the research study (you can use a color to distinguish beteen either treated/never-treated or based on the time when the municipalty gets the teratment, with a lighter color for those municiaplities that started the program at the beginning of the sample and darker and darker for all the others).
I want to see also the federal state bounderies (in order to understand in whihc federal state the municipality is located)
Use leaflet fucntion to create the map.
- if i click on a specific municipality, I want to see:
    1. the municipality name
    2. the code
    3. the dates when it staretd the program (and if it stopped and if eventually it started again)

- if i clik on a municipality, on the right of the shiny app, I want to see on the top the relevant dates for the program (when it started, if it eneded, if it staretd again) and down I want to see a plot where i can see a MA of the daily registration + daily registration in the background in grey + verticla lines for the dates of the program

- i want you to create the series in the plot using ggiraph package, so i can interact with it.




**Libraries (necessary)**:

```{r}
if (!require("pacman")) install.packages("pacman")
pacman::p_load(
  here,        # here()
  arrow,       # open_dataset(), read_parquet(), write_parquet(), collect()
  sfarrow,     # st_read_parquet()
  sf,          # st_drop_geometry()
  dplyr,       # rename, mutate, case_when, if_else, left_join, relocate,
               # filter, select, group_by, summarise, arrange, pull, ungroup, n
  tibble,      # tibble()
  tidyr,       # complete()
  lubridate,   # floor_date()
  stringr,     # str_pad()
  restatis     # gen_logincheck(), gen_table()
)
```



# 1. datasets
> Here there is a list of the datasets you can use to create the shiny app.


## 1.1. treatment dataset
> Here you can see the municipalities in the sample I want to use, with the treatment path for each of them.

**Importnat**: when you decide to add new municipalities, please update the dataset in chapter 1.2.

Dataset:

```{r}
# Full date range
all_dates <- seq.Date(as.Date("2019-02-01"), as.Date("2025-11-01"), by = "month")

# All municipalities (Survey names take priority over Ben names for overlapping codes)
muni_all <- tribble(
  ~Municipality,                    ~MunicipalityCode,
  # From Survey
  "Bonn, Stadt",                    "05314000",
  "Darmstadt, Wissenschaftsstadt",  "06411000",
  "Frankfurt am Main, Stadt",       "06412000",
  "Oldenburg (Oldenburg), Stadt",   "03403000",
  "Jever, Stadt",                   "03455007",
  "Fröndenberg/Ruhr, Stadt",        "05978012",
  "Weilheim i.OB, St",             "09190157",
  "Kamp-Lintfort, Stadt",          "05170020",
  "Lüneburg, Hansestadt",           "03355022",
  "Friedrichshafen, Stadt",         "08435016",
  "Kornwestheim, Stadt",            "08118046",
  "Erlangen",                       "09562000",
  "Wickede (Ruhr)",                 "05974056",
  # From Heidelberg
  "Heidelberg, Stadt",              "08221000",
  # From Ben (not in Survey)
  "Stuttgart",                      "08111000",
  "Koln",                           "05315000",
  "Braunschweig",                   "03101000",
  "Munchen",                        "09162000",
  "Berlin",                         "11000000",
  "Essen",                          "05113000",
  "Dresden",                        "14612000",
  "Duisburg",                       "05112000",
  "Dortmund",                       "05913000",
  "Bremen",                         "04011000",
  "Bremerhaven",                    "04012000",
  "Hamburg",                         "02000000",
  "Reutlingen",                     "08415061",
  "Erfurt",                         "16051000",
  "Hannover",                       "03241001",
  "Munster",                        "05515000"
)

# Create full balanced panel
data.treatment <- crossing(
  MunicipalityCode = muni_all$MunicipalityCode,
  date = all_dates
) |>
  left_join(muni_all, by = "MunicipalityCode") |>
  mutate(
    treatment = case_when(
      # --- Survey municipalities (priority 1) ---
      MunicipalityCode == "05314000" & date >= as.Date("2021-09-01") ~ 1L,
      MunicipalityCode == "06411000" & date >= as.Date("2021-07-01") ~ 1L,
      MunicipalityCode == "06412000" & date >= as.Date("2023-11-01") & date <= as.Date("2024-03-01") ~ 1L,
      MunicipalityCode == "03403000" & date >= as.Date("2020-01-01") & date <= as.Date("2023-03-01") ~ 1L,
      MunicipalityCode == "03455007" & date >= as.Date("2023-01-01") & date <= as.Date("2023-12-01") ~ 1L,
      MunicipalityCode == "05978012" & date >= as.Date("2022-03-01") & date <= as.Date("2023-12-01") ~ 1L,
      MunicipalityCode == "09190157" & date >= as.Date("2022-04-01") & date <= as.Date("2024-12-01") ~ 1L,
      MunicipalityCode == "05170020" & date >= as.Date("2021-11-01") & date <= as.Date("2024-03-01") ~ 1L,
      # --- Heidelberg (priority 2) ---
      MunicipalityCode == "08221000" & date >= as.Date("2022-09-01") & date <= as.Date("2024-03-01") ~ 1L,
      # --- Ben-only municipalities (priority 3) ---
      MunicipalityCode == "08111000" & date >= as.Date("2020-11-01") & date <= as.Date("2025-12-01") ~ 1L,
      MunicipalityCode == "05315000" & date >= as.Date("2022-04-01") ~ 1L,
      MunicipalityCode == "03101000" & date >= as.Date("2022-04-01") ~ 1L,
      MunicipalityCode == "09162000" & date >= as.Date("2022-10-01") ~ 1L,
      MunicipalityCode == "11000000" & date >= as.Date("2023-02-01") ~ 1L,
      MunicipalityCode == "05113000" & date >= as.Date("2023-03-01") ~ 1L,
      MunicipalityCode == "14612000" & date >= as.Date("2023-06-01") ~ 1L,
      MunicipalityCode == "05112000" & date >= as.Date("2023-10-01") ~ 1L,
      MunicipalityCode == "05913000" & date >= as.Date("2023-11-01") ~ 1L,
      TRUE ~ 0L
    )
  ) |>
  select(Municipality, MunicipalityCode, date, treatment) |>
  arrange(Municipality, MunicipalityCode, date) |>
  group_by(MunicipalityCode) |>
  mutate(ever_treated = max(treatment)) |>
  ungroup()


```


Save and load the treatment dataset:

```{r}
write_parquet(
  data.treatment,
  here("3. subsidy programs/3.4. shiny app/2. shiny apps/2/data.treatment.parquet")
)

data.treatment <- read_parquet(
  here("3. subsidy programs/3.4. shiny app/2. shiny apps/2/data.treatment.parquet")
)
```


## 1.2. Dataset of daily registrations
> here there is the dataset to see the daily registration of balcony PVs over time.

**Important**: sometimes I will update the treatment dataset and I will add some new municipalities. So, update this dataset accordingly.

Create the datasets:
```{r}
data <- open_dataset(here("3. subsidy programs/3.1. data/EinheitenSolar.parquet"))


# Step 1: rename German → English (explicit mapping, column order differs from old dataset)
data <- data |>
  rename(
    UnitMastrNumber                          = EinheitMastrNummer,
    DateLastUpdate                           = DatumLetzteAktualisierung,
    LocationMastrNumber                      = LokationMaStRNummer,
    GridOperatorVerificationStatus           = NetzbetreiberpruefungStatus,
    GridOperatorVerificationDate             = NetzbetreiberpruefungDatum,
    PlantOperatorMastrNumber                 = AnlagenbetreiberMastrNummer,
    Country                                  = Land,
    FederalState                             = Bundesland,
    District                                 = Landkreis,
    Municipality                             = Gemeinde,
    MunicipalityCode                         = Gemeindeschluessel,
    PostalCode                               = Postleitzahl,
    City                                     = Ort,
    RegistrationDate                         = Registrierungsdatum,
    CommissioningDate                        = Inbetriebnahmedatum,
    UnitSystemStatus                         = EinheitSystemstatus,
    UnitOperationalStatus                    = EinheitBetriebsstatus,
    NotPresentInMigratedUnits                = NichtVorhandenInMigriertenEinheiten,
    PowerGenerationUnitName                  = NameStromerzeugungseinheit,
    Weic_NotAvailable                        = Weic_nv,
    PowerPlantNumber_NotAvailable            = Kraftwerksnummer_nv,
    EnergySource                             = Energietraeger,
    GrossCapacity                            = Bruttoleistung,
    NetNominalCapacity                       = Nettonennleistung,
    RemoteControllabilityGridOperator        = FernsteuerbarkeitNb,
    FeedInType                               = Einspeisungsart,
    AssignedActivePowerInverter              = ZugeordneteWirkleistungWechselrichter,
    NumberOfModules                          = AnzahlModule,
    TypeOfSolarSystem                        = ArtDerSolaranlage,
    PowerLimitation                          = Leistungsbegrenzung,
    UniformOrientationAndTiltAngle           = EinheitlicheAusrichtungUndNeigungswinkel,
    MainOrientation                          = Hauptausrichtung,
    MainOrientationTiltAngle                 = HauptausrichtungNeigungswinkel,
    UsageArea                                = Nutzungsbereich,
    EegMastrNumber                           = EegMaStRNummer,
    StorageAtSameLocation                    = SpeicherAmGleichenOrt,
    SecondaryOrientation                     = Nebenausrichtung,
    SecondaryOrientationTiltAngle            = NebenausrichtungNeigungswinkel,
    Street                                   = Strasse,
    StreetNotFound                           = StrasseNichtGefunden,
    HouseNumber_NotAvailable                 = Hausnummer_nv,
    HouseNumberNotFound                      = HausnummerNichtGefunden,
    Longitude                                = Laengengrad,
    Latitude                                 = Breitengrad,
    DateStartTemporaryDecommissioning        = DatumBeginnVoruebergehendeStilllegung,
    HouseNumber                              = Hausnummer,
    AddressAddition                          = Adresszusatz,
    RemoteControllabilityDirectMarketer      = FernsteuerbarkeitDv,
    PreviousPlantOperatorMastrNumber         = AltAnlagenbetreiberMastrNummer,  # new variable
    DateOfOperatorChange                     = DatumDesBetreiberwechsels,
    DateRegistrationOfOperatorChange         = DatumRegistrierungDesBetreiberwechsels,
    CadastralDistrict                        = Gemarkung,
    FieldParcelNumbers                       = FlurFlurstuecknummern,
    ConnectionToExtraHighOrHighVoltage       = AnschlussAnHoechstOderHochSpannung,
    DatePermanentDecommissioning             = DatumEndgueltigeStilllegung,
    SizeOfUsedAreaInHectares                 = GroesseDerInAnspruchGenommenenFlaecheInHektar,
    PreviousUsageTypeOfArea                  = VorherigerNutzungsartenbereichDerFlaeche,
    PredominantUsageTypeBeforeSolarConstruction = UeberwiegendeNutzungsartDerFlaecheVorErrichtung,
    NameOfSolarPark                          = NameDesSolarparks,
    AdditionalFeaturesOfAreaAndCurrentUsage  = ZusaetzlicheMerkmaleDerFlaecheUndDerAktuellenFlaechennutzung,
    GenMastrNumber                           = GenMastrNummer,
    CommissioningDateAtCurrentLocation       = InbetriebnahmedatumAmAktuellenStandort,
    DispatchResponsible                      = Einsatzverantwortlicher,
    CitizenEnergy                            = Buergerenergie,
    DateResumptionOfOperation                = DatumWiederaufnahmeBetrieb,
    PlannedCommissioningDate                 = GeplantesInbetriebnahmedatum,
    ClearanceHeight                          = LichteHoehe,
    PowerPlantNumber                         = Kraftwerksnummer
  )

# Step 2: convert numeric columns (XML parsing stores everything as character)
data <- data |>
  mutate(
    TypeOfSolarSystem           = as.integer(TypeOfSolarSystem),
    Country                     = as.integer(Country),
    FederalState                = as.integer(FederalState),
    GrossCapacity               = as.numeric(GrossCapacity),
    NetNominalCapacity          = as.numeric(NetNominalCapacity),
    AssignedActivePowerInverter = as.numeric(AssignedActivePowerInverter),
    NumberOfModules             = as.integer(NumberOfModules)
  )

# Step 3: lookup tables
C1 <- data.frame(
  TypeOfSolarSystem.names = c(
    "Structural_facilities", "Other_Structural_facilities", "Open_space",
    "Bodies_water", "Large_parking_lot", "Plug_in_sola_system", "Onshore&Offshore_wind_power"
  ),
  TypeOfSolarSystem = as.integer(c(853, 2484, 852, 3002, 3058, 2961, NA))
)

C2 <- tibble(
  Country = as.integer(c(84, 231, 90, 66, 198, 206, 106)),
  Country.sn = c("Germany", "Switzerland", "Denmark", "Belgium", "Netherlands", "Austria", "France")
)

C3 <- data.frame(
  FederalState = as.integer(c(
    1409, 1402, 1400, 1403, 1412, 1408, 1410, 1407,
    1414, 1411, 1413, 1405, 1415, 1406, 1401, 1404
  )),
  FederalState.names = c(
    "North Rhine-Westphalia", "Baden-Württemberg", "Brandenburg", "Bavaria",
    "Saarland", "Lower Saxony", "Rhineland-Palatinate", "Mecklenburg-Western Pomerania",
    "Saxony-Anhalt", "Schleswig-Holstein", "Saxony", "Hesse",
    "Thuringia", "Hamburg", "Berlin", "Bremen"
  ),
  FederalStateCode = c(
    "DEA", "DE1", "DE4", "DE2",
    "DEC", "DE9", "DEB", "DEM",
    "DEE", "DEF", "DED", "DE7",
    "DEG", "DE6", "DE3", "DE5"
  )
)

# district code from map (no geometry needed)
districts_map <- st_read_parquet(here("ignore/2. maps/districts.parquet")) |>
  st_drop_geometry() |>
  select(District, DistrictCode)

# Step 4: join lookups
data <- data |>
  left_join(C1, by = "TypeOfSolarSystem") |>
  relocate(TypeOfSolarSystem.names, .after = TypeOfSolarSystem) |>
  left_join(C2, by = "Country") |>
  relocate(Country.sn, .after = Country) |>
  left_join(C3, by = "FederalState") |>
  relocate(FederalState.names, .after = FederalState) |>
  relocate(FederalStateCode, .after = FederalState.names) |>
  left_join(districts_map, by = "District") |>
  relocate(DistrictCode, .after = District)

# Step 5: solar_category
reform_date <- as.Date("2024-05-16")

data <- data |>
  mutate(
    RegistrationDate  = as.Date(RegistrationDate),
    CommissioningDate = as.Date(CommissioningDate),
    solar_category = case_when(
      TypeOfSolarSystem == 2961 & RegistrationDate <  reform_date & AssignedActivePowerInverter <= 0.6 ~ "Plug_in_sola_system - Balcony",
      TypeOfSolarSystem == 2961 & RegistrationDate >= reform_date & AssignedActivePowerInverter <= 0.8 & GrossCapacity <= 2.0 ~ "Plug_in_sola_system - Balcony",
      TypeOfSolarSystem == 2961 ~ "Plug_in_sola_system - Non-Balcony",
      TRUE ~ TypeOfSolarSystem.names
    )
  )
# Step 6: filter Germany
data <- data |>
  filter(Country.sn == "Germany")

# Step 7: date variables (week, month, quarter, year)
data <- data |>
  mutate(
    date.registration.day     = RegistrationDate,
    date.registration.week    = floor_date(RegistrationDate,  "week"),
    date.registration.month   = floor_date(RegistrationDate,  "month"),
    date.registration.quarter = floor_date(RegistrationDate,  "quarter"),
    date.registration.year    = floor_date(RegistrationDate,  "year"),
    date.commission.day       = CommissioningDate,
    date.commission.week      = floor_date(CommissioningDate, "week"),
    date.commission.month     = floor_date(CommissioningDate, "month"),
    date.commission.quarter   = floor_date(CommissioningDate, "quarter"),
    date.commission.year      = floor_date(CommissioningDate, "year")
  )

# Step 8: fix MunicipalityCode
data <- data |>
  mutate(MunicipalityCode = str_pad(as.character(MunicipalityCode), 8, pad = "0"))
```

Collapse every category other than `Balcony PVs` into a single `Non-balcony PVs` group:

```{r}
data <- data |>
  mutate(solar_category = if_else(solar_category == "Plug_in_sola_system - Balcony",
                                  "Balcony PVs",
                                  "Non-balcony PVs"))
```


Here I want to filter for the balcony PVs:

```{r}
data <- data |>
  filter(solar_category == "Balcony PVs")
```

I want to filter based on the municipalities I chose for the treatment dataset:

```{r}
data <- data |>
  filter(MunicipalityCode %in% muni_all$MunicipalityCode)
```


Create the dataset daily frequency for all municipalities:

```{r}
data_day <- data |>
  group_by(MunicipalityCode, Municipality, date.registration.day) |>
  summarise(n = n(), .groups = "drop") |>
  collect() |>
  group_by(MunicipalityCode, Municipality) |>
  complete(date.registration.day = seq(min(date.registration.day), max(date.registration.day), by = "day"), fill = list(n = 0)) |>
  arrange(MunicipalityCode, date.registration.day) |>
  mutate(n_cumulative = cumsum(n)) |>
  ungroup()
```

***Population***:

```{r}
#Credentials:
# gen_auth_save(database = 'genesis')
# gen_auth_save(database = 'regio')

gen_logincheck(database = "genesis")
gen_logincheck(database = "regio")


# Load the data:
pop.muni.2023 <- gen_table(
  name      = "12411-01-01-5",
  database  = "regio",
  language  = "en",
  startyear = 2023,
  endyear   = 2023
) |>
  filter(`1_variable_code` == "GEMEIN",          # municipalities only (drops DINSG/DLAND/REGBEZ/KREISE)
         is.na(`2_variable_attribute_code`)) |>  # sex total
  select(
    MunicipalityCode = `1_variable_attribute_code`,
    Municipality     = `1_variable_attribute_label`,
    year             = time,
    population       = value
  ) |>
  mutate(
    date       = as.Date(paste0(substr(year, 1, 4), "-12-31")),
    population = suppressWarnings(as.numeric(population))
  ) |>
  select(Municipality, MunicipalityCode, date, population) 
```


**Save**:
```{r}

write_parquet(
  pop.muni.2023,
  here("3. subsidy programs/3.4. shiny app/1. data/pop.muni.2023.parquet")
)
```

***Adjust for the population data***:

```{r}
# population data only for the relevant municipalities
# (distinct() drops duplicate rows produced by hidden GENESIS dimensions)
pop.muni.2023 <- pop.muni.2023 |>
  filter(MunicipalityCode %in% muni_all$MunicipalityCode) |>
  distinct()

data_day <- data_day |>
  left_join(pop.muni.2023 |> select(MunicipalityCode, population),
            by = "MunicipalityCode") |>
  mutate(
    n_per100k            = (n            / population) * 100000,
    n_cumulative_per100k = (n_cumulative / population) * 100000
  )
```

***load the dataset***:

```{r}
write_parquet(
  data_day,
  here("3. subsidy programs/3.4. shiny app/2. shiny apps/2/outcome_variable.parquet")
)

data_day <- read_parquet(
  here("3. subsidy programs/3.4. shiny app/2. shiny apps/2/outcome_variable.parquet")
)
```





## 1.3. dataset for bounderies
> Here I want to load the datasets for the bounderis, i.e., for municipalities and federal states.

**Dataset for municipalities**:

```{r}
municipalities <- st_read_parquet(here("ignore", "2. maps", "municipalities.parquet"))
glimpse(municipalities)
```



**Dataset for federal states**:

```{r}
federal_states <- st_read_parquet(here("ignore", "2. maps", "federalState.parquet"))
glimpse(federal_states)
```



# 2. shiny app
> Here I want you to create the shiny app I mentioned at the beginning. Please do everything in one chunk, where you have both the usre interface and the server in the same chunk (so that once I run, it elaborate everything).

Shiny app:
```{r}
# extra libraries used only by the app
pacman::p_load(shiny, leaflet, ggplot2, ggiraph, slider, htmltools, purrr)

# --- 1. pre-compute treatment episodes (runs of treatment == 1) per muni -----
treatment_episodes <- data.treatment |>
  arrange(MunicipalityCode, date) |>
  group_by(MunicipalityCode) |>
  mutate(
    new_episode = treatment == 1L & lag(treatment, default = 0L) == 0L,
    episode_id  = cumsum(new_episode)
  ) |>
  filter(treatment == 1L) |>
  group_by(MunicipalityCode, Municipality, episode_id) |>
  summarise(start = min(date), end = max(date), .groups = "drop") |>
  arrange(MunicipalityCode, start) |>
  select(MunicipalityCode, Municipality, start, end)

# first start date per muni (NA = never treated) — used for map colouring
muni_start <- data.treatment |>
  filter(treatment == 1L) |>
  group_by(MunicipalityCode) |>
  summarise(first_start = min(date), .groups = "drop")

# --- 2. build the sf for the map ---------------------------------------------
muni_sf <- municipalities |>
  filter(MunicipalityCode %in% muni_all$MunicipalityCode) |>
  left_join(muni_start, by = "MunicipalityCode")

pal <- colorNumeric(
  palette  = "viridis",
  domain   = as.numeric(muni_sf$first_start),
  na.color = "#bbbbbb",
  reverse  = TRUE   # earlier starts -> lighter, later starts -> darker
)

# --- 3. UI -------------------------------------------------------------------
ui <- fluidPage(
  titlePanel("Balcony-PV subsidy programs — daily registrations by municipality"),
  fluidRow(
    column(6, leafletOutput("map", height = 720)),
    column(6,
      uiOutput("muni_info"),
      sliderInput("ma_window", "Moving-average window (days):",
                  min = 7, max = 90, value = 30, step = 1),
      girafeOutput("plot", height = "480px")
    )
  )
)

# --- 4. server ---------------------------------------------------------------
server <- function(input, output, session) {

  output$map <- renderLeaflet({
    leaflet() |>
      addProviderTiles(providers$CartoDB.Positron) |>
      addPolygons(
        data    = federal_states,
        fill    = FALSE,
        color   = "black",
        weight  = 2,
        opacity = 0.7
      ) |>
      addPolygons(
        data        = muni_sf,
        layerId     = ~MunicipalityCode,
        fillColor   = ~pal(as.numeric(first_start)),
        fillOpacity = 0.85,
        color       = "white",
        weight      = 1,
        label       = ~paste0(Municipality, " (", MunicipalityCode, ")"),
        highlightOptions = highlightOptions(weight = 3, color = "red", bringToFront = TRUE)
      ) |>
      addLegend(
        position  = "bottomright",
        pal       = pal,
        values    = as.numeric(muni_sf$first_start),
        title     = "Treatment start",
        labFormat = labelFormat(transform = function(x)
          format(as.Date(x, origin = "1970-01-01"), "%Y-%m")),
        na.label  = "Never treated"
      )
  })

  selected_code <- reactive({ input$map_shape_click$id })

  output$muni_info <- renderUI({
    code <- selected_code()
    if (is.null(code)) return(tags$p(em("Click a municipality on the map.")))
    info <- muni_all |> filter(MunicipalityCode == code)
    ep   <- treatment_episodes |> filter(MunicipalityCode == code)
    tagList(
      tags$h4(info$Municipality),
      tags$p(tags$strong("Code: "), code),
      tags$strong("Program episodes:"),
      if (nrow(ep) == 0) tags$p(em("Never treated")) else
        tags$ul(
          purrr::pmap(list(ep$start, ep$end), function(s, e)
            tags$li(format(s, "%Y-%m-%d"), " → ", format(e, "%Y-%m-%d"))
          )
        )
    )
  })

  output$plot <- renderGirafe({
    code <- selected_code()
    if (is.null(code)) return(NULL)
    d <- data_day |>
      filter(MunicipalityCode == code) |>
      arrange(date.registration.day)
    if (nrow(d) == 0) return(NULL)
    d <- d |> mutate(
      ma = slider::slide_dbl(n, mean,
                             .before = input$ma_window - 1L,
                             .complete = FALSE)
    )
    ep <- treatment_episodes |> filter(MunicipalityCode == code)

    g <- ggplot(d, aes(x = date.registration.day)) +
      geom_col(aes(y = n), fill = "grey80") +
      geom_line_interactive(
        aes(y = ma,
            tooltip = paste0(format(date.registration.day, "%Y-%m-%d"),
                             "  |  daily n = ", n,
                             "  |  MA = ", round(ma, 1)),
            data_id = as.character(date.registration.day)),
        colour = "steelblue", linewidth = 0.8
      )
    if (nrow(ep) > 0) {
      g <- g +
        geom_vline(data = ep, aes(xintercept = as.numeric(start)),
                   colour = "darkgreen", linetype = "dashed") +
        geom_vline(data = ep, aes(xintercept = as.numeric(end)),
                   colour = "darkred", linetype = "dashed")
    }
    g <- g +
      labs(x = NULL, y = "Daily registrations",
           title    = paste0(unique(d$Municipality), " — ", code),
           subtitle = paste0(input$ma_window, "-day moving average  ·  ",
                             "green = program start, red = program end")) +
      theme_minimal()

    girafe(ggobj = g, width_svg = 8, height_svg = 4,
           options = list(opts_hover(css = "stroke:orange;stroke-width:1.5;")))
  })
}

shinyApp(ui, server)
```