---
title: 'Replicate Deryugina (2017)'
format: html
---



> Here I want to replicate Deryugina (2017).

Libraries:

```{r}
pacman::p_load(
  here, haven, polars,           # paths & Stata I/O
  tidyverse,              # dplyr, ggplot2, tidyr, purrr, readr
  fixest,                 # TWFE / event-study regressions with FE
  modelsummary,           # regression tables
  broom,                  # tidy model output
  DIDmultiplegt,          # de Chaisemartin & D'Haultfœuille static
  DIDmultiplegtDYN        # de Chaisemartin & D'Haultfœuille dynamic
)

pacman::p_load(
  tidyverse, arrow, here, knitr,
  DIDmultiplegtSTAT
)

```

Libraries (necessary):

```{r}
pacman::p_load(haven, dplyr, DIDmultiplegtDYN, polars)

```

# 1. load the dataset and prepare data
> Here I want to load the dataset and prepare it for running regressions (with covariates too).

Dataset:

```{r}
data <- read_dta(here("2. Replications", "02_01 Datasets", "Deryugina (2017)", "deryugina_2017.dta"))
data |> print() |> glimpse()
```


How many obs:

```{r}
n_distinct(data$county_fips)
```


Plot outcome variable:

```{r}
data |>
  ggplot(aes(x = year, y = log_curr_trans_ind_gov_pc, group = county_fips)) +
  geom_line() +
  geom_point() +
  labs(
    x = "Year",
    y = "Mean log per-capita gov. transfers to individuals"
  ) +
  theme_minimal()
```

Treatment over time:

```{r}
data |>
  group_by(county_fips) |>
  mutate(first_hurr = suppressWarnings(min(year[hurricane == 1], na.rm = TRUE))) |>
  ungroup() |>
  mutate(
    first_hurr = ifelse(is.infinite(first_hurr), NA, first_hurr),
    county_order = rank(first_hurr, ties.method = "first", na.last = "keep")
  ) |>
  ggplot(aes(x = year, y = reorder(factor(county_fips), county_order), fill = factor(hurricane))) +
  geom_tile() +
  scale_fill_manual(values = c("0" = "grey90", "1" = "firebrick"), name = "Hurricane") +
  labs(x = "Year", y = "County (sorted by first hurricane year)") +
  theme_minimal() +
  theme(axis.text.y = element_blank(), axis.ticks.y = element_blank())

# simple plot
ggplot(data, aes(year, factor(county_fips), fill = factor(hurricane))) +
  geom_tile()
```

I want to test if the design STAY holds or not (I want to create a function for this; and also for STAY-C):

> **Design STAY** — $\exists\ (g, g')$ such that:
> **(i)** $D_{g,1} = D_{g',1}$ (same baseline treatment),
> **(ii)** $F_g \neq F_{g'}$ (different first-switch periods, where $F_g = \infty$ if $g$ never switches).

```{r}
check_stay <- function(df, group, time, treat) {

  df <- df |> arrange(.data[[group]], .data[[time]])

  units <- df |>
    group_by(.data[[group]]) |>
    summarise(
      D1 = first(.data[[treat]]),
      F  = {
        sw <- which(.data[[treat]] != dplyr::lag(.data[[treat]]))
        if (length(sw) == 0) Inf else .data[[time]][min(sw)]
      },
      .groups = "drop"
    )

  # (i) at least two groups share the same baseline treatment D_{g,1}
  cond_i  <- any(table(units$D1) >= 2)

  # (ii) at least two groups have different first-switch periods F_g
  cond_ii <- dplyr::n_distinct(units$F) >= 2

  # STAY design holds iff (i) AND (ii) hold simultaneously for some pair
  pair_exists <- units |>
    dplyr::group_by(D1) |>
    dplyr::summarise(n_F = dplyr::n_distinct(F), .groups = "drop") |>
    dplyr::filter(n_F >= 2) |>
    nrow() > 0

  list(
    `(i) same baseline D_{g,1}`        = cond_i,
    `(ii) different first-switch F_g`  = cond_ii,
    `STAY design holds`                = pair_exists
  )
}

check_stay(data, group = "county_fips", time = "year", treat = "hurricane")
```

Here show me the code without fucntion:


```{r}
units <- data |>
  arrange(county_fips, year) |>
  group_by(county_fips) |>
  summarise(
    D1 = first(hurricane),
    F  = {
      sw <- which(hurricane != lag(hurricane))
      if (length(sw) == 0) Inf else year[min(sw)]
    },
    .groups = "drop"
  )

units
table(units$D1, units$F) 
units |>
  ggplot(aes(x = F, group = D1, color = D1))+
  geom_bar()

units |>
  group_by(D1, F) |>
  summarise(n = n()) |>
  ggplot(aes(x = F, y = n, group = factor(D1), fill = factor(D1)))+
  geom_col()
```


# 2. DID estimators
> Here I want to show the DID estimators.

Dataset:

```{r}
data
```

## 2.1. TWFE model
> Here I want to run a TWFE model and show the estimates.

Static TWFE:

Run three specifications so we can compare them side by side:

```{r}
m1 <- feols(log_curr_trans_ind_gov_pc ~ hurricane | county_fips + year,
            data = data, cluster = ~county_fips)

m2 <- feols(log_curr_trans_ind_gov_pc ~ hurricane + log_pop1969 |
              county_fips + year,
            data = data, cluster = ~county_fips)
```


Table:

```{r}
etable(m1, m2,
       headers = c("Baseline", "+ pop control"),
       signif.code = c("***" = 0.01, "**" = 0.05, "*" = 0.1))
       
modelsummary(
  list(
    "TWFE"            = m1,
    "+ pop control"   = m2 ),
  stars   = TRUE,
  gof_map = c("nobs", "r.squared", "FE: county_fips", "FE: year"),
  output  = "markdown"
)


```


Event study (leads -5 to -2, current, lags 1 to 10; lead -1 omitted as reference):

```{r}
data_es <- data |>
  group_by(county_fips) |>
  mutate(
    first_hurr_year = suppressWarnings(min(year[hurricane == 1], na.rm = TRUE)),
    first_hurr_year = ifelse(is.infinite(first_hurr_year), NA, first_hurr_year),
    time_to_hurr   = year - first_hurr_year,
    time_to_hurr   = ifelse(is.na(time_to_hurr), -1000, time_to_hurr),  # never-treated bucket
    time_to_hurr   = pmin(pmax(time_to_hurr, -5), 10)                    # bin endpoints
  ) |>
  ungroup()

data_es |> print() |> glimpse()

es <- feols(
  log_curr_trans_ind_gov_pc ~ i(time_to_hurr, ref = c(-1, -1000)) |
    county_fips + year,
  data    = data_es,
  cluster = ~county_fips
)

iplot(es,
      xlab     = "Years since first hurricane",
      main     = "Event study: effect of hurricane on log gov. transfers pc",
      ref.line = 0)
```


## 2.2. static model
> Here I want to apply the de Chaisemartin & D'Haultfœuille static estimator (`did_multiplegt_stat`), which is valid for non-absorbing treatment under the STAY-C design.

```{r}
stat <- did_multiplegt_stat(
  df        = data,
  Y   = "log_curr_trans_ind_gov_pc",
  ID     = "county_fips",
  Time      = "year",
  D = "hurricane",
  exact_match = TRUE,
  estimator = c("aoss", "waoss"),
  switchers = NULL,
  disaggregate = NULL,
  placebo      = TRUE
)

stat
```


## 2.3. dynamic model
> Here I want to estimate the model assuming dynamic effect of the treatment.

Model1:

```{r}
res_t2 <- did_multiplegt_dyn(
  df        = data,
  outcome   = "log_curr_trans_ind_gov_pc",
  group     = "county_fips",
  time      = "year",
  treatment = "hurricane",
  effects   = 11,
  placebo   = 11,
  cluster   = "county_fips"
)
print(res_t2)
res_t2$plot
```


## 2.4. Test dynamic effect of the treatment
> here I want to test the dynamic effect of the treatment.

Test:

```{r}
test1 <- did_multiplegt_dyn(
  df        = data,
  outcome   = "log_curr_trans_ind_gov_pc",
  group     = "county_fips",
  time      = "year",
  treatment = "hurricane",
  effects   = 5,
  placebo   = 5,
  cluster   = "county_fips",
  effects_equal = TRUE,
  same_switchers = TRUE
)


```