---
title: "Dataset (clean, transferable)"
format: html
---


# How to use this file

This file generates panel datasets (monthly / quarterly / yearly) for a
difference-in-differences analysis on municipality-level data.

**Single source of truth:** all municipality info — name, AGS code,
treatment start date, treatment end date — lives in **one tibble**
(`muni_treatment` below). Everything downstream is derived from it.

**To add or remove a municipality:** edit `muni_treatment` only. Re-run.
- Always-treated tail: leave `treatment_end = NA`.
- Never-treated control: set `treatment_start = NA, treatment_end = NA`.

**To change the save location:** edit `output_path` at the top.

**To change the panel date range:** edit `date_from` / `date_to`.

**To change the source files:** edit `mastr_path` and `districts_path`.

Outputs (three parquets) — same column schema across frequencies:
- `Municipality`, `MunicipalityCode`, `date`, `year`
- Outcome: `n_installations`, `population`, `n_installations_per_1000`,
           `n_installations_cumulative`, `n_installations_cumulative_per_1000`
- Treatment: `treatment`, `ever_treated`
- Covariate: `income_per_capita_eur` (time-invariant; build year × cov
             interactions at regression time via `fixest::i(year, income_per_capita_eur, ref = …)`).


# 1. Setup

Libraries:

```{r}
pacman::p_load(tidyverse, arrow, sfarrow, sf, here, knitr, restatis)
```

Credentials (uncomment the first run to register the regio API key):

```{r}
# gen_auth_save(database = "regio")
gen_logincheck(database = "regio")
```



# 2. Municipality list (single source of truth)

Each row = one municipality in the sample. Treatment dates use **monthly
granularity** (first day of the month). For always-treated tails or never-
treated controls, leave `treatment_end` (or both) as `NA`.



# 3. dataset 

## 3.1. dataset monhtly
```{r}
muni_treatment <- tribble(
  ~Municipality,                    ~MunicipalityCode, ~treatment_start, ~treatment_end,
  # From Survey
  "Bonn, Stadt",                    "05314000",        "2021-09-01",     NA,
  "Darmstadt, Wissenschaftsstadt",  "06411000",        "2021-07-01",     NA,
  "Frankfurt am Main, Stadt",       "06412000",        "2023-11-01",     "2024-03-01",
  "Oldenburg (Oldenburg), Stadt",   "03403000",        "2020-01-01",     "2023-03-01",
  "Jever, Stadt",                   "03455007",        "2023-01-01",     "2023-12-01",
  "Fröndenberg/Ruhr, Stadt",        "05978012",        "2022-03-01",     "2023-12-01",
  "Weilheim i.OB, St",              "09190157",        "2022-04-01",     "2024-12-01",
  "Kamp-Lintfort, Stadt",           "05170020",        "2021-11-01",     "2024-03-01",
  "Lüneburg, Hansestadt",           "03355022",        NA,               NA,
  "Friedrichshafen, Stadt",         "08435016",        NA,               NA,
  "Kornwestheim, Stadt",            "08118046",        NA,               NA,
  "Erlangen",                       "09562000",        NA,               NA,
  "Wickede (Ruhr)",                 "05974056",        NA,               NA,
  # From Heidelberg
  "Heidelberg, Stadt",              "08221000",        "2022-09-01",     "2024-03-01",
  # From Ben (not in Survey)
  "Stuttgart",                      "08111000",        "2020-11-01",     "2025-12-01",
  "Koln",                           "05315000",        "2022-04-01",     NA,
  "Braunschweig",                   "03101000",        "2022-04-01",     NA,
  "Munchen",                        "09162000",        "2022-10-01",     NA,
  "Berlin",                         "11000000",        "2023-02-01",     NA,
  "Essen",                          "05113000",        "2023-03-01",     NA,
  "Dresden",                        "14612000",        "2023-06-01",     NA,
  "Duisburg",                       "05112000",        "2023-10-01",     NA,
  "Dortmund",                       "05913000",        "2023-11-01",     NA,
  "Bremen",                         "04011000",        NA,               NA,
  "Bremerhaven",                    "04012000",        NA,               NA,
  "Hamburg",                        "02000000",        NA,               NA,
  "Reutlingen",                     "08415061",        NA,               NA,
  "Erfurt",                         "16051000",        NA,               NA,
  "Hannover",                       "03241001",        NA,               NA,
  "Munster",                        "05515000",        NA,               NA
) |>
  mutate(
    treatment_start = as.Date(treatment_start),
    treatment_end   = as.Date(treatment_end)
  )

muni_treatment
```


Unique chucnk:

```{r}
# ============================================================================
# (1) TREATMENT PANEL — monthly balanced panel of (muni, date) with treatment
# ============================================================================

# Full monthly date range for the panel
all_dates <- seq.Date(as.Date("2019-02-01"), as.Date("2026-05-07"), by = "month")

# Municipality list (Survey names take priority over Ben names for overlapping codes)
muni_all <- tribble(
  ~Municipality,                    ~MunicipalityCode,
  # From Survey
  "Bonn, Stadt",                    "05314000",
  "Darmstadt, Wissenschaftsstadt",  "06411000",
  "Frankfurt am Main, Stadt",       "06412000",
  "Oldenburg (Oldenburg), Stadt",   "03403000",
  "Jever, Stadt",                   "03455007",
  "Fröndenberg/Ruhr, Stadt",        "05978012",
  "Weilheim i.OB, St",             "09190157",
  "Kamp-Lintfort, Stadt",          "05170020",
  "Lüneburg, Hansestadt",           "03355022",
  "Friedrichshafen, Stadt",         "08435016",
  "Kornwestheim, Stadt",            "08118046",
  "Erlangen",                       "09562000",
  "Wickede (Ruhr)",                 "05974056",
  # From Heidelberg
  "Heidelberg, Stadt",              "08221000",
  # From Ben (not in Survey)
  "Stuttgart",                      "08111000",
  "Koln",                           "05315000",
  "Braunschweig",                   "03101000",
  "Munchen",                        "09162000",
  "Berlin",                         "11000000",
  "Essen",                          "05113000",
  "Dresden",                        "14612000",
  "Duisburg",                       "05112000",
  "Dortmund",                       "05913000",
  "Bremen",                         "04011000",
  "Bremerhaven",                    "04012000",
  "Hamburg",                         "02000000",
  "Reutlingen",                     "08415061",
  "Erfurt",                         "16051000",
  "Hannover",                       "03241001",
  "Munster",                        "05515000"
)

# Create full balanced panel
data.treatment <- crossing(
  MunicipalityCode = muni_all$MunicipalityCode,
  date = all_dates
) |>
  left_join(muni_all, by = "MunicipalityCode") |>
  mutate(
    treatment = case_when(
      # --- Survey municipalities (priority 1) ---
      MunicipalityCode == "05314000" & date >= as.Date("2021-09-01") ~ 1L,
      MunicipalityCode == "06411000" & date >= as.Date("2021-07-01") ~ 1L,
      MunicipalityCode == "06412000" & date >= as.Date("2023-11-01") & date <= as.Date("2024-03-01") ~ 1L,
      MunicipalityCode == "03403000" & date >= as.Date("2020-01-01") & date <= as.Date("2023-03-01") ~ 1L,
      MunicipalityCode == "03455007" & date >= as.Date("2023-01-01") & date <= as.Date("2023-12-01") ~ 1L,
      MunicipalityCode == "05978012" & date >= as.Date("2022-03-01") & date <= as.Date("2023-12-01") ~ 1L,
      MunicipalityCode == "09190157" & date >= as.Date("2022-04-01") & date <= as.Date("2024-12-01") ~ 1L,
      MunicipalityCode == "05170020" & date >= as.Date("2021-11-01") & date <= as.Date("2024-03-01") ~ 1L,
      # --- Heidelberg (priority 2) ---
      MunicipalityCode == "08221000" & date >= as.Date("2022-09-01") & date <= as.Date("2024-03-01") ~ 1L,
      # --- Ben-only municipalities (priority 3) ---
      MunicipalityCode == "08111000" & date >= as.Date("2020-11-01") & date <= as.Date("2025-12-01") ~ 1L,
      MunicipalityCode == "05315000" & date >= as.Date("2022-04-01") ~ 1L,
      MunicipalityCode == "03101000" & date >= as.Date("2022-04-01") ~ 1L,
      MunicipalityCode == "09162000" & date >= as.Date("2022-10-01") ~ 1L,
      MunicipalityCode == "11000000" & date >= as.Date("2023-02-01") ~ 1L,
      MunicipalityCode == "05113000" & date >= as.Date("2023-03-01") ~ 1L,
      MunicipalityCode == "14612000" & date >= as.Date("2023-06-01") ~ 1L,
      MunicipalityCode == "05112000" & date >= as.Date("2023-10-01") ~ 1L,
      MunicipalityCode == "05913000" & date >= as.Date("2023-11-01") ~ 1L,
      TRUE ~ 0L
    )
  ) |>
  select(Municipality, MunicipalityCode, date, treatment) |>
  arrange(Municipality, MunicipalityCode, date) |>
  group_by(MunicipalityCode) |>
  mutate(ever_treated = max(treatment)) |>
  ungroup()


# ============================================================================
# (2) LOAD AND CLEAN THE RAW MaStR DUMP
# ============================================================================

# Open the raw Marktstammdatenregister parquet (lazy Arrow dataset)
data <- open_dataset(here("9. dataset", "EinheitenSolar_all.parquet"))


# Step 2.1: rename German → English
# (explicit mapping; column order differs from older versions of the dump)
data <- data |>
  rename(
    UnitMastrNumber                          = EinheitMastrNummer,
    DateLastUpdate                           = DatumLetzteAktualisierung,
    LocationMastrNumber                      = LokationMaStRNummer,
    GridOperatorVerificationStatus           = NetzbetreiberpruefungStatus,
    GridOperatorVerificationDate             = NetzbetreiberpruefungDatum,
    PlantOperatorMastrNumber                 = AnlagenbetreiberMastrNummer,
    Country                                  = Land,
    FederalState                             = Bundesland,
    District                                 = Landkreis,
    Municipality                             = Gemeinde,
    MunicipalityCode                         = Gemeindeschluessel,
    PostalCode                               = Postleitzahl,
    City                                     = Ort,
    RegistrationDate                         = Registrierungsdatum,
    CommissioningDate                        = Inbetriebnahmedatum,
    UnitSystemStatus                         = EinheitSystemstatus,
    UnitOperationalStatus                    = EinheitBetriebsstatus,
    NotPresentInMigratedUnits                = NichtVorhandenInMigriertenEinheiten,
    PowerGenerationUnitName                  = NameStromerzeugungseinheit,
    Weic_NotAvailable                        = Weic_nv,
    PowerPlantNumber_NotAvailable            = Kraftwerksnummer_nv,
    EnergySource                             = Energietraeger,
    GrossCapacity                            = Bruttoleistung,
    NetNominalCapacity                       = Nettonennleistung,
    RemoteControllabilityGridOperator        = FernsteuerbarkeitNb,
    FeedInType                               = Einspeisungsart,
    AssignedActivePowerInverter              = ZugeordneteWirkleistungWechselrichter,
    NumberOfModules                          = AnzahlModule,
    TypeOfSolarSystem                        = ArtDerSolaranlage,
    PowerLimitation                          = Leistungsbegrenzung,
    UniformOrientationAndTiltAngle           = EinheitlicheAusrichtungUndNeigungswinkel,
    MainOrientation                          = Hauptausrichtung,
    MainOrientationTiltAngle                 = HauptausrichtungNeigungswinkel,
    UsageArea                                = Nutzungsbereich,
    EegMastrNumber                           = EegMaStRNummer,
    StorageAtSameLocation                    = SpeicherAmGleichenOrt,
    SecondaryOrientation                     = Nebenausrichtung,
    SecondaryOrientationTiltAngle            = NebenausrichtungNeigungswinkel,
    Street                                   = Strasse,
    StreetNotFound                           = StrasseNichtGefunden,
    HouseNumber_NotAvailable                 = Hausnummer_nv,
    HouseNumberNotFound                      = HausnummerNichtGefunden,
    Longitude                                = Laengengrad,
    Latitude                                 = Breitengrad,
    DateStartTemporaryDecommissioning        = DatumBeginnVoruebergehendeStilllegung,
    HouseNumber                              = Hausnummer,
    AddressAddition                          = Adresszusatz,
    RemoteControllabilityDirectMarketer      = FernsteuerbarkeitDv,
    PreviousPlantOperatorMastrNumber         = AltAnlagenbetreiberMastrNummer,  # new variable
    DateOfOperatorChange                     = DatumDesBetreiberwechsels,
    DateRegistrationOfOperatorChange         = DatumRegistrierungDesBetreiberwechsels,
    CadastralDistrict                        = Gemarkung,
    FieldParcelNumbers                       = FlurFlurstuecknummern,
    ConnectionToExtraHighOrHighVoltage       = AnschlussAnHoechstOderHochSpannung,
    DatePermanentDecommissioning             = DatumEndgueltigeStilllegung,
    SizeOfUsedAreaInHectares                 = GroesseDerInAnspruchGenommenenFlaecheInHektar,
    PreviousUsageTypeOfArea                  = VorherigerNutzungsartenbereichDerFlaeche,
    PredominantUsageTypeBeforeSolarConstruction = UeberwiegendeNutzungsartDerFlaecheVorErrichtung,
    NameOfSolarPark                          = NameDesSolarparks,
    AdditionalFeaturesOfAreaAndCurrentUsage  = ZusaetzlicheMerkmaleDerFlaecheUndDerAktuellenFlaechennutzung,
    GenMastrNumber                           = GenMastrNummer,
    CommissioningDateAtCurrentLocation       = InbetriebnahmedatumAmAktuellenStandort,
    DispatchResponsible                      = Einsatzverantwortlicher,
    CitizenEnergy                            = Buergerenergie,
    DateResumptionOfOperation                = DatumWiederaufnahmeBetrieb,
    PlannedCommissioningDate                 = GeplantesInbetriebnahmedatum,
    ClearanceHeight                          = LichteHoehe,
    PowerPlantNumber                         = Kraftwerksnummer
  )

# Step 2.2: coerce numeric columns (XML parsing stores everything as character)
data <- data |>
  mutate(
    TypeOfSolarSystem           = as.integer(TypeOfSolarSystem),
    Country                     = as.integer(Country),
    FederalState                = as.integer(FederalState),
    GrossCapacity               = as.numeric(GrossCapacity),
    NetNominalCapacity          = as.numeric(NetNominalCapacity),
    AssignedActivePowerInverter = as.numeric(AssignedActivePowerInverter),
    NumberOfModules             = as.integer(NumberOfModules)
  )

# Step 2.3: lookup tables (TypeOfSolarSystem, Country, FederalState, District)
C1 <- data.frame(
  TypeOfSolarSystem.names = c(
    "Structural_facilities", "Other_Structural_facilities", "Open_space",
    "Bodies_water", "Large_parking_lot", "Plug_in_sola_system", "Onshore&Offshore_wind_power"
  ),
  TypeOfSolarSystem = as.integer(c(853, 2484, 852, 3002, 3058, 2961, NA))
)

C2 <- tibble(
  Country = as.integer(c(84, 231, 90, 66, 198, 206, 106)),
  Country.sn = c("Germany", "Switzerland", "Denmark", "Belgium", "Netherlands", "Austria", "France")
)

C3 <- data.frame(
  FederalState = as.integer(c(
    1409, 1402, 1400, 1403, 1412, 1408, 1410, 1407,
    1414, 1411, 1413, 1405, 1415, 1406, 1401, 1404
  )),
  FederalState.names = c(
    "North Rhine-Westphalia", "Baden-Württemberg", "Brandenburg", "Bavaria",
    "Saarland", "Lower Saxony", "Rhineland-Palatinate", "Mecklenburg-Western Pomerania",
    "Saxony-Anhalt", "Schleswig-Holstein", "Saxony", "Hesse",
    "Thuringia", "Hamburg", "Berlin", "Bremen"
  ),
  FederalStateCode = c(
    "DEA", "DE1", "DE4", "DE2",
    "DEC", "DE9", "DEB", "DEM",
    "DEE", "DEF", "DED", "DE7",
    "DEG", "DE6", "DE3", "DE5"
  )
)

# District code from map (geometry dropped — only the District ↔ code lookup is needed)
districts_map <- st_read_parquet(here("9. dataset", "districts.parquet")) |>
  st_drop_geometry() |>
  select(District, DistrictCode)

# Step 2.4: attach lookup labels and codes to the dataset
data <- data |>
  left_join(C1, by = "TypeOfSolarSystem") |>
  relocate(TypeOfSolarSystem.names, .after = TypeOfSolarSystem) |>
  left_join(C2, by = "Country") |>
  relocate(Country.sn, .after = Country) |>
  left_join(C3, by = "FederalState") |>
  relocate(FederalState.names, .after = FederalState) |>
  relocate(FederalStateCode, .after = FederalState.names) |>
  left_join(districts_map, by = "District") |>
  relocate(DistrictCode, .after = District)

# Step 2.5: classify balcony PVs (Solarpaket-I reform on 2024-05-16 changed the threshold)
reform_date <- as.Date("2024-05-16")

data <- data |>
  mutate(
    RegistrationDate  = as.Date(RegistrationDate),
    CommissioningDate = as.Date(CommissioningDate),
    solar_category = case_when(
      TypeOfSolarSystem == 2961 & RegistrationDate <  reform_date & AssignedActivePowerInverter <= 0.6 ~ "Plug_in_sola_system - Balcony",
      TypeOfSolarSystem == 2961 & RegistrationDate >= reform_date & AssignedActivePowerInverter <= 0.8 & GrossCapacity <= 2.0 ~ "Plug_in_sola_system - Balcony",
      TypeOfSolarSystem == 2961 ~ "Plug_in_sola_system - Non-Balcony",
      TRUE ~ TypeOfSolarSystem.names
    )
  )
# Step 2.6: keep Germany only
data <- data |>
  filter(Country.sn == "Germany")

# Step 2.7: derive date variables at every frequency we may need downstream
data <- data |>
  mutate(
    date.registration.day     = RegistrationDate,
    date.registration.week    = floor_date(RegistrationDate,  "week"),
    date.registration.month   = floor_date(RegistrationDate,  "month"),
    date.registration.quarter = floor_date(RegistrationDate,  "quarter"),
    date.registration.year    = floor_date(RegistrationDate,  "year"),
    date.commission.day       = CommissioningDate,
    date.commission.week      = floor_date(CommissioningDate, "week"),
    date.commission.month     = floor_date(CommissioningDate, "month"),
    date.commission.quarter   = floor_date(CommissioningDate, "quarter"),
    date.commission.year      = floor_date(CommissioningDate, "year")
  )

# Step 2.8: pad MunicipalityCode to 8 digits (preserve leading zeros)
data <- data |>
  mutate(MunicipalityCode = str_pad(as.character(MunicipalityCode), 8, pad = "0"))


# ============================================================================
# (3) FILTER TO BALCONY PVs IN TREATMENT MUNICIPALITIES, INSIDE THE PANEL RANGE
# ============================================================================

# Keep balcony PVs only
data <- data |>
  filter(solar_category == "Plug_in_sola_system - Balcony")

# Single source of truth: the muni list comes from data.treatment above.
# Any change to data.treatment automatically propagates downstream.
muni_all <- data.treatment |>
  distinct(Municipality, MunicipalityCode)

# Keep only the treatment municipalities
data <- data |>
  filter(MunicipalityCode %in% muni_all$MunicipalityCode)

# Restrict to the monthly panel range
lo <- min(all_dates)
hi <- max(all_dates)
data <- data |>
  filter(date.registration.month >= lo,
         date.registration.month <= hi)


# ============================================================================
# (4) AGGREGATE TO MONTHLY OUTCOME PANEL (balanced, with cumulative stock)
# ============================================================================

data.outcome <- data |>
  count(MunicipalityCode, date = date.registration.month, name = "n_installations") |>
  collect() |>
  complete(
    MunicipalityCode = muni_all$MunicipalityCode,
    date             = all_dates,
    fill             = list(n_installations = 0L)
  ) |>
  left_join(muni_all, by = "MunicipalityCode") |>
  arrange(MunicipalityCode, date) |>
  group_by(MunicipalityCode) |>
  mutate(n_installations_cumulative = cumsum(n_installations)) |>
  ungroup() |>
  select(Municipality, MunicipalityCode, date,
         n_installations, n_installations_cumulative)


# ============================================================================
# (5) POPULATION DENOMINATOR (2023, from Destatis regio)
# ============================================================================

pop_2023 <- gen_table(
  name      = "12411-01-01-5",
  database  = "regio",
  language  = "en",
  startyear = 2023,
  endyear   = 2023
) |>
  filter(`1_variable_code` == "GEMEIN",                # municipalities only
         is.na(`2_variable_attribute_code`),           # sex Total
         !is.na(`1_variable_attribute_label`),         # drop unnamed rows
         !value %in% c("-", ".")) |>                   # drop Destatis sentinels (- / .)
  transmute(
    Municipality     = `1_variable_attribute_label`,
    MunicipalityCode = `1_variable_attribute_code`,
    population_2023  = as.numeric(value)
  )

# Population-adjust the outcome (flow and cumulative stock, per 1,000 inhabitants)
data.outcome <- data.outcome |>
  left_join(pop_2023 |> select(MunicipalityCode, population_2023),
            by = "MunicipalityCode") |>
  rename(population = population_2023) |>
  mutate(
    n_installations_per_1000            = n_installations            / population * 1000,
    n_installations_cumulative_per_1000 = n_installations_cumulative / population * 1000
  )


# ============================================================================
# (6) COVARIATE: 2018 INCOME PER CAPITA (time-invariant)
# ============================================================================

# 2018 total income — Gesamtbetrag der Einkünfte (EKF002), in Tsd. EUR → EUR
income_2018 <- gen_table(
  name      = "73111-01-01-5",
  database  = "regio",
  language  = "en",
  startyear = 2018,
  endyear   = 2018
) |>
  filter(`1_variable_code` == "GEMEIN",                # municipalities only
         value_variable_code == "EKF002",              # total income (drops LSNW01/LSNW02)
         !is.na(`1_variable_attribute_label`),
         !value %in% c("-", ".")) |>
  transmute(
    Municipality     = `1_variable_attribute_label`,
    MunicipalityCode = `1_variable_attribute_code`,
    total_income_eur = as.numeric(value) * 1000        # Tsd. EUR -> EUR
  )

# 2018 population — denominator for per-capita income
# (fresh 2018 snapshot, not the 2023 figure, so the ratio is internally consistent)
pop_2018 <- gen_table(
  name      = "12411-01-01-5",
  database  = "regio",
  language  = "en",
  startyear = 2018,
  endyear   = 2018
) |>
  filter(`1_variable_code` == "GEMEIN",
         is.na(`2_variable_attribute_code`),
         !is.na(`1_variable_attribute_label`),
         !value %in% c("-", ".")) |>
  transmute(
    Municipality     = `1_variable_attribute_label`,
    MunicipalityCode = `1_variable_attribute_code`,
    population_2018  = as.numeric(value)
  )

# Income per capita = total income / population (joined on AGS)
income_pc_2018 <- income_2018 |>
  inner_join(pop_2018 |> select(MunicipalityCode, population_2018),
             by = "MunicipalityCode") |>
  mutate(income_per_capita_eur = total_income_eur / population_2018) |>
  select(Municipality, MunicipalityCode, income_per_capita_eur)


# ============================================================================
# (7) MERGE — outcome (panel) + treatment (panel) + income covariate (invariant)
# ============================================================================
# The covariate is broadcast to every month by joining on MunicipalityCode only.
# `year` is added so year × covariate interactions can be built at regression
# time via fixest::i(year, income_per_capita_eur, ref = ...).

data.merged <- data.outcome |>
  left_join(data.treatment |> select(MunicipalityCode, date, treatment, ever_treated),
            by = c("MunicipalityCode", "date")) |>
  left_join(income_pc_2018 |> select(MunicipalityCode, income_per_capita_eur),
            by = "MunicipalityCode") |>
  mutate(year = year(date)) |>
  arrange(MunicipalityCode, date)

data.merged |> print() |> glimpse()

```


Save it:

```{r}
# save to disk
write_parquet(
  data.merged,
  here("9. dataset", "data_monthly.parquet")
)

# reload (verification) and inspect
data.monthly <- read_parquet(
  here("9. dataset", "data_monthly.parquet")
)

data.monthly |> print() |> glimpse()
```



